### 2016-10-20 paper/evaluation.tex
Working on RQs

\newcommand{\RQONE}{How prevalent is the occurence of costly
regression tests?}
\newcommand{\rqOne}{\textbf{RQ1.} \RQONE}

\newcommand{\RQTWO}{\Fix{...}}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQTWO{}}

\newcommand{\RQTHREE}{\Fix{...}}
\newcommand{\rqThree}{\textbf{RQ3.} \RQTHREE{}}

\newcommand{\RQFOUR}{How often developers use \Fix{...} to
improve performance on test execution?}
\newcommand{\rqFour}{\textbf{RQ4.} \RQFOUR{}}

\newcommand{\RQFIVE}{\Fix{...}}
\newcommand{\rqFive}{\textbf{RQ5.} \RQFIVE{}}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
    \item \rqThree
    \item \rqFour
    \item \rqFive
\end{itemize}

\Fix{describe what I'm looking for with these RQs}

@@

We used the Github's Search API to fetch the top 1.000 projects in
Java with at least 100 stars. The number of stars indicates the
interest and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation for relevant projects
to conduct our study. For each project, we detected the build manager
system based on the files located in the root directory (\eg,
\emph{pom.xml}) from the project in the following precedence:
\textsc{Maven}, \textsc{Gradle}, and \textsc{Ant}. From the 1.000
downloaded projects, we automatically detected the build system from
806 subjects and selected the \Fix{154} projects that we were able to
compile.  The full list of subjects is publicly available at
\Fix{...}.

@@

\begin{itemize}
    \item \RQONE
\end{itemize}

To evaluate the frequency of costly \Jbc{How to define "costly" in
terms of time?}regression tests, we first compiled the project and
test source files, later, we measured the elapsed time to run the
tests via the build system ignoring non-related tasks (\eg,
\emph{javadoc} generation).  We grouped the resulting time from test
executions in four different groups: tests that ran in less than one
minute (group A), one to five minutes (group B), five to ten minutes
(group C), and more than ten minutes to execute (group D).
Figure~\ref{fig:timecost-barplot} shows the distribution of subjects
per group. It is important to mention that
Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

@@

>>>>

\newcommand{\RQONE}{How prevalent is the occurence of time-consuming
regression tests in open-source projects?}
\newcommand{\RQTWO}{What is the distribution of CPU and IO bound
regression tests from the sample set?}
\newcommand{\RQTHREE}{What is the proportion of \Fix{time-consuming?}
test cases per project?}
\newcommand{\RQFOUR}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

\newcommand{\rqA}{\textbf{RQ1.} \RQONE}
\newcommand{\rqB}{\textbf{RQ2.} \RQTWO}
\newcommand{\rqC}{\textbf{RQ3.} \RQTHREE}
\newcommand{\rqD}{\textbf{RQ4.} \RQFOUR}

\begin{itemize}
    \item \rqA
    \item \rqB
    \item \rqC
    \item \rqD
\end{itemize}

The first research question addresses the distribution of subjects per
elapsed time to execute regression tests. We are interested on
identifying time-consuming test suites for further investigation. The
second research question addresses addresses \Fix{...}. The third
research question addresses the distribution of \Fix{...}. Finally,
the fourth research question investigates the relevance of supporting
parallel execution on builder tools.

@@

We used the Github's Search API to fetch the top 1.000 projects in
Java with at least 100 stars. The number of stars indicates the
interest and appreciation from the community to a given project.
\Comment{(https://help.github.com/articles/about-stars/)} Although our
criteria is subjective, it is an approximation for relevant projects
to conduct our study. For each project, we detected the build manager
system based on the files located in the root directory (\eg,
\emph{pom.xml}) from the project in the following precedence: Maven,
Gradle, and Ant. From the 1.000 downloaded projects, we automatically
detected the build system from 806 subjects and selected the \Fix{154}
projects that we were able to compile.

\subsection{Setup and Replication}
\label{sec:setup}

To run our experiments we used a Core i7-4790 (3.60GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running on Ubuntu 14.04 LTS (64-bit
version). \Fix{add Vagrantfile with software settings} All the source
artifacts, including supporting scripts (\eg, the script that test
subjects and generates the raw data), and the full list of projects
are publicly available at \Fix{...}.

@@

%% \begin{itemize}
%%     \item \RQONE
%% \end{itemize}

To evaluate the frequency of costly regression tests, we first
compiled the project and test source files, later, we measured the
elapsed time to run the tests via the build system ignoring
non-related tasks (\eg, \emph{javadoc} generation).  We grouped the
resulting time from test executions into four different groups: tests
that ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{normal execution}), five to ten minutes (\emph{long
execution}), and more than ten minutes to execute (\emph{very long
execution}).  Figure~\ref{fig:timecost-barplot} shows the distribution
of subjects per group. It is important to mention that
Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

@@

\subsection{Answering research question RQ2}
\label{sec:rqtwo}

%% \begin{itemize}
%%     \item \RQTWO
%% \end{itemize}

\Fix{to appear...}

\subsection{Answering research question RQ3}
\label{sec:rqthree}

%% \begin{itemize}
%%     \item \RQTHREE
%% \end{itemize}

\Fix{to appear...}

\subsection{Answering research question RQ4}
\label{sec:rqfour}

%% \begin{itemize}
%%     \item \RQFOUR
%% \end{itemize}

\Fix{to appear...}
